Verifying Demonstrations

### 2017-11-17 contents-poster.tex
Refactors poster
- Adds figure of Trumps inauguration fiasco.
- Adds where other methods are failing.

@@

    \begin{redblock}{Verifying protest participation}
      \begin{itemize}
        \item Alice wants to show that many support her cause.
        \item Eve wants to show that few support Alice's cause.
        \item \color{red} Adversarial setting, requires verifiable results!
      \end{itemize}
    \end{redblock}

    \begin{figure}
      \centering
      \includegraphics[width=0.9\linewidth]{fig/Jacobs-method.jpg}
      \caption{%
        Jacobs Method, currently most used method.
        Divide into regions, estimate density in each region, sum up.
        Image: popularmechanics.com
      }\label{JacobsMethod}
    \end{figure}

@@

@@

\vspace{5em}

@@

    \begin{figure}
      \centering
      \begin{tikzpicture}[%
        -Latex,
        item/.style={rectangle,draw},
        edge from parent/.style={},
        ]
        \tikzset{%
          %grow'=left,%
          %level distance=5em%
        }
        \node[item] (proof) {Proof share}
        child {%
          node[item] (pid) {$pid$}
          child {%
            node[item] (cid) {$cid$}
            child {%
              node[item] (manifesto) {Manifesto}
            }
          }
        }
        child {%
          node[item] (wid) {$wid$}
        }
        child {%
          node[item] (ts) {$t_s$}
        }
        child {%
          node[item] (l) {$l$}
        }
        child {%
          node[item] (wsig) {$wsig$}
        }
        ;

@@

@@

    \begin{block}{More info}
      \begin{center}
        \includegraphics[width=0.4\linewidth]{fig/qr.eps}
      \end{center}
    \end{block}

@@

\flushright
Special thanks to xkcd.com who, over many years, has inspired the stylistic 
presentation of this poster.

>>>>

\vfill

@@

    \begin{redblock}{Verifying protest participation}
      \begin{itemize}
        \item Alice wants to show that many support her cause.
        \item Eve wants to show that few support Alice's cause.
        \item {\color{red} Adversarial setting, requires verifiable results!}
          (E.g.\ \cref{TrumpInauguration}.)
      \end{itemize}
    \end{redblock}

@@

    \begin{figure}
      \centering
      \includegraphics[width=0.9\linewidth]{fig/trump.jpg}
      \caption{%
        What can we trust?
        (Hint: not much.)
        Image: Reddit/The\_Donald, Twitter.
      }\label{TrumpInauguration}
    \end{figure}

@@

\vfill

@@

  \begin{column}{0.32\linewidth}
    \begin{figure}
      \centering
      \begin{tikzpicture}[%
        -Latex,
        item/.style={rectangle,draw},
        edge from parent/.style={},
        ]
        \tikzset{%
          %grow'=left,%
          %level distance=5em%
        }
        \node[item] (proof) {Proof share}
        child {%
          node[item] (pid) {$pid$}
          child {%
            node[item] (cid) {$cid$}
            child {%
              node[item] (manifesto) {Manifesto}
            }
          }
        }
        child {%
          node[item] (wid) {$wid$}
        }
        child {%
          node[item] (ts) {$t_s$}
        }
        child {%
          node[item] (l) {$l$}
        }
        child {%
          node[item] (wsig) {$wsig$}
        }
        ;

@@

    \begin{block}{More info}
      \centering
      \includegraphics[width=0.4\linewidth]{fig/qr.eps}
    \end{block}

@@

    \begin{figure}
      \centering
      \includegraphics[width=\linewidth]{fig/Jacobs-method.jpg}
      \caption{%
        Jacobs Method, currently most used method.
        Divide into regions, estimate density in each region, sum up.
        Image: popularmechanics.com
      }\label{JacobsMethod}
    \end{figure}

    \begin{purpleblock}{Current crowd-counting methods}
      \begin{itemize}
        \item Most used method, Jacobs Method (\cref{JacobsMethod}).
        \item {\color{red} Cannot handle cumulative counts, faces problems 
            illustrated by \cref{TrumpInauguration}.}
        \item Computer vision does object recognition; requires photos/video 
          that cover the entire location, all the time.
        \item {\color{red} This will still count people twice.}
        \item Scan active mobile phones (or similar) in the area.
        \item This requires some extra equipment.
        \item {\color{red} This catches bystanders who are not protesting.}
        \item {\color{red} Neither method can distinguish two close but 
            different protests (e.g.\ pro- and anti-protests).}
      \end{itemize}
    \end{purpleblock}

@@

\flushright
Special thanks to xkcd.com which, over many years, has inspired the stylistic 
presentation of this poster.
